Create Figures and Tables

### 2023-08-30 Codes/0_2_quickstat.Rmd
minor updates

---
title: "Get crop yield and acreage data: Corn and Soybeans"
author: "Taro Mieno"
output:
  html_document:
    number_sections: yes
    theme: flatly
    highlight: zenburn
    toc_float: yes
    toc: yes
    toc_depth: 3
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  tidy = FALSE,
  cache.lazy = FALSE,
  #--- figure ---#
  dpi = 400,
  fig.width = 7.5,
  fig.height = 5,
  out.width = "750px",
  out.height = "500px"
)
```

@@

```{r }
get_quickstat_data <- function(year, data_item) {
  desc <-
    tidyUSDA::allDataItem %>%
    grep(pattern = data_item, ., value = TRUE) %>%
    .[!grepl(., pattern = "NET")]

  temp_data <- getQuickstat(
    key = key_get("usda_nass_qs_api"),
    program = "SURVEY",
    data_item = desc,
    geographic_level = "COUNTY",
    state = all_states,
    year = year,
    geometry = FALSE
  ) %>%
    #--- keep only some of the variables ---#
    dplyr::select(year, county_code, state_fips_code, short_desc, Value) %>%
    rename("state_code" = "state_fips_code")

@@

```{r }
item_list <-
  c(
    "CORN, GRAIN, IRRIGATED - YIELD",
    "CORN, GRAIN, NON-IRRIGATED - YIELD",
    "CORN, GRAIN, IRRIGATED - ACRES HARVESTED",
    "CORN, GRAIN, NON-IRRIGATED - ACRES HARVESTED",
    "SOYBEANS, IRRIGATED - YIELD",
    "SOYBEANS, NON-IRRIGATED - YIELD",
    "SOYBEANS, IRRIGATED - ACRES HARVESTED",
    "SOYBEANS, NON-IRRIGATED - ACRES HARVESTED"
  )
```

@@

```{r }
(
  par_list <-
    expand.grid(
      data_item = item_list,
      year = as.character(1985:2018)
    ) %>%
    data.table()
)
```

@@

```{r download-nass-data, eval = F}

# === Download the relevant NASS data ===#
(
  nass_data <-
    lapply(
      seq_len(nrow(par_list)),
      function(x) {
        print(x)
        data <- get_quickstat_data(
          par_list[x, year],
          par_list[x, data_item]
        ) %>%
          data.table()
        return(data)
      }
    ) %>%
    rbindlist()
)

>>>>

---
title: "Get crop yield and acreage data: Corn and Soybeans"
---

@@

```{r }
get_quickstat_data <- function(year, data_item) {
  desc <-
    tidyUSDA::allDataItem %>%
    grep(pattern = data_item, ., value = TRUE)

  temp_data <-
    tidyUSDA::getQuickstat(
      key = key_get("usda_nass_qs_api"),
      program = "SURVEY",
      data_item = desc,
      geographic_level = "COUNTY",
      state = all_states,
      year = year,
      geometry = FALSE
    ) %>%
    #--- keep only some of the variables ---#
    dplyr::select(year, county_code, state_fips_code, short_desc, Value) %>%
    rename("state_code" = "state_fips_code")

@@

```{r }
item_list <-
  c(
    "CORN, GRAIN, IRRIGATED - YIELD, MEASURED IN BU / ACRE",
    "CORN, GRAIN, NON-IRRIGATED - YIELD, MEASURED IN BU / ACRE",
    "CORN, GRAIN, IRRIGATED - ACRES HARVESTED",
    "CORN, GRAIN, NON-IRRIGATED - ACRES HARVESTED",
    "SOYBEANS, IRRIGATED - YIELD, MEASURED IN BU / ACRE",
    "SOYBEANS, NON-IRRIGATED - YIELD, MEASURED IN BU / ACRE",
    "SOYBEANS, IRRIGATED - ACRES HARVESTED",
    "SOYBEANS, NON-IRRIGATED - ACRES HARVESTED"
  )

# tidyUSDA::allDataItem %>%
#     grep(pattern = "PLANTED", ., value = TRUE) %>%
#     grep(pattern = "SOYBEANS", ., value = TRUE) %>%
#     grep(pattern = "IRRIGATED", ., value = TRUE)

# for (i in 1:length(item_list)) {
#   desc <-
#     tidyUSDA::allDataItem %>%
#     grep(pattern = data_item, ., value = TRUE)
#   print(desc)
# }
```

@@

```{r }
par_list <-
  data.table::CJ(
    data_item = item_list,
    year = as.character(1985:2018)
  )
```

@@

```{r download-nass-data, eval = F}
nass_data <-
  lapply(
    seq_len(nrow(par_list)),
    function(x) {
      print(x)
      data <-
        get_quickstat_data(
          year = par_list[x, year],
          data_item = par_list[x, data_item]
        ) %>%
        data.table()
      return(data)
    }
  )

### 2023-08-30 Codes/1_Analysis.rmd
minor updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE,
  tidy = FALSE,
  cache.lazy = FALSE,
  #--- figure ---#
  dpi = 400,
  fig.width = 7.5,
  fig.height = 5,
  out.width = "750px",
  out.height = "500px"
)
```

@@

#--- Data used for regression analysis ---#
reg_data <-
  prepare_reg_data(
    data = final_data,
    sat_thld_m = 9, # saturated thickness has to be at least 12 meters
    ir_share_thld = 0.75, # at least 75% of total county area has to be overlapped with HPA
    balance_thld = c(-1200, 200),
    sat_cat_num = 3,
    state_ls =
      list(
        corn = c("CO", "KS", "NE", "NM", "SD", "TX", "WY"),
        soy = c("KS", "NE", "TX")
      )
  ) %>%
  data.table() %>%
  setnames("crop_type", "crop")

@@

main_analysis <-
  reg_data %>%
  rowwise() %>%
  dplyr::mutate(sc_base = "31011") %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(balance_seq = list(
    seq(
      min(data$balance),
      max(data$balance),
      length = 100
    )
  )) %>%
  dplyr::mutate(sat_seq_eval = list(
    c(10, 50, 90, 130)
  )) %>%
  dplyr::mutate(share_reg_data = list(
    data %>%
      .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
      .[, balance_avg := mean(balance), by = sc_code]
  )) %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(sat_seq = list(
    share_reg_data[, seq(min(sat),
      max(sat),
      length = 100
    )] %>%
      c(., sat_seq_eval)
  )) %>%
  #--- values of the controls to be used in prediction ---#
  dplyr::mutate(
    sandtotal_med = median(share_reg_data$sandtotal_r),
    silttotal_med = median(share_reg_data$silttotal_r),
    awc_med = median(share_reg_data$awc_r)
  ) %>%
  #++++++++++++++++++++++++++++++++++++
  #+ Main analysis
  #++++++++++++++++++++++++++++++++++++
  dplyr::mutate(yield_analysis_results = list(
    yield_analysis(data, balance_seq, sat_seq_eval, sat_breaks, sat_text_data, sc_base)
  )) %>%
  dplyr::mutate(
    yield_pred_data = list(yield_analysis_results$yield_pred_data),
    yield_semi_res = list(yield_analysis_results$semi_res)
  ) %>%
  dplyr::mutate(yield_dif_test = list(
    lapply(
      2:3,
      \(x) {
        test_dif_in_yield(
          balance_ls = seq(min(data$balance), max(data$balance), length = 50),
          base_q = 1,
          comp_q = x,
          yield_semi_res,
          sat_text_data,
          sc_base
        ) %>%
          .[, comp_q := x]
      }
    ) %>%
      rbindlist()
  )) %>%
  dplyr::mutate(share_pred_data = list(
    share_analysis(share_reg_data, sat_seq, sandtotal_med, silttotal_med, awc_med)
  )) %>%
  dplyr::mutate(avg_yield_pred_data = list(
    get_average_yield(yield_pred_data, share_pred_data)
  ))

@@

all_results <-
  main_analysis %>%
  #--- bootsrap data ---#
  dplyr::mutate(boot_results = list(
    parallel::mclapply(
      1:1000,
      \(x) {
        print(x)

@@

        #--- share analysis ---#
        share_boot_data <-
          boot_data %>%
          .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
          .[, balance_avg := mean(balance), by = sc_code]

>>>>

@@

#--- Data used for regression analysis ---#
reg_data <-
  prepare_reg_data(
    data = final_data,
    #--- saturated thickness has to be at least 9 meters ---#
    sat_thld_m = 9, 
    #--- at least 75% of total county area has to be overlapped with HPA ---#
    ir_share_thld = 0.75, 
    #--- drop obs with extreme balance ---#
    balance_thld = c(-1200, 200),
    #--- number of saturated thickness categories ---#
    sat_cat_num = 3,
    #--- select states of focus ---#
    # no observations are dropped with the current set of states 
    state_ls =
      list(
        corn = c("CO", "KS", "NE", "NM", "SD", "TX", "WY"),
        soy = c("KS", "NE", "TX")
      )
  ) %>%
  data.table() %>%
  setnames("crop_type", "crop")

@@

# main_analysis$share_reg_data[[1]]
# main_analysis$share_reg_data[[2]]

main_analysis <-
  reg_data %>%
  rowwise() %>%
  dplyr::mutate(sc_base = "31011") %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(balance_seq = list(
    seq(
      min(data$balance),
      max(data$balance),
      length = 100
    )
  )) %>%
  dplyr::mutate(sat_seq_eval = list(
    c(10, 50, 90, 130)
  )) %>%
  dplyr::mutate(share_reg_data = list(
    data %>%
      .[, comp := sum(ir == "nir" | ir == "ir"), by = .(sc_code, year)] %>%
      .[comp == 2, ] %>%
      .[, acres_ratio := acres / sum(acres), by = .(sc_code, year)] %>%
      .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
      .[, balance_avg := mean(balance), by = sc_code]
  )) %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(sat_seq = list(
    share_reg_data[, seq(min(sat),
      max(sat),
      length = 100
    )] %>%
      c(., sat_seq_eval)
  )) %>%
  #--- values of the controls to be used in prediction ---#
  dplyr::mutate(
    sandtotal_med = median(share_reg_data$sandtotal_r),
    silttotal_med = median(share_reg_data$silttotal_r),
    awc_med = median(share_reg_data$awc_r)
  ) %>%
  #++++++++++++++++++++++++++++++++++++
  #+ Main analysis
  #++++++++++++++++++++++++++++++++++++
  dplyr::mutate(yield_analysis_results = list(
    yield_analysis(data, balance_seq, sat_seq_eval, sat_breaks, sat_text_data, sc_base)
  )) %>%
  dplyr::mutate(
    yield_pred_data = list(yield_analysis_results$yield_pred_data),
    yield_semi_res = list(yield_analysis_results$semi_res)
  ) %>%
  dplyr::mutate(yield_dif_test = list(
    lapply(
      2:3,
      \(x) {
        test_dif_in_yield(
          balance_ls = seq(min(data$balance), max(data$balance), length = 50),
          base_q = 1,
          comp_q = x,
          yield_semi_res,
          sat_text_data,
          sc_base
        ) %>%
          .[, comp_q := x]
      }
    ) %>%
      rbindlist()
  )) %>%
  dplyr::mutate(share_pred_data = list(
    share_analysis(
      share_reg_data, 
      sat_seq, 
      sandtotal_med, 
      silttotal_med, 
      awc_med, 
      crop
    )
  )) %>%
  dplyr::mutate(avg_yield_pred_data = list(
    get_average_yield(yield_pred_data, share_pred_data)
  ))

@@

all_results <-
  main_analysis %>%
  #--- bootsrap data ---#
  dplyr::mutate(boot_results = list(
    parallel::mclapply(
      1:200,
      \(x) {
        print(x)

@@

        #--- share analysis ---#
        share_boot_data <-
          boot_data %>%
          .[, comp := sum(ir == "nir" | ir == "ir"), by = .(sc_code, year)] %>%
          .[comp == 2, ] %>%
          .[, acres_ratio := acres / sum(acres), by = .(sc_code, year)] %>%
          .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
          .[, balance_avg := mean(balance), by = sc_code]

### 2023-08-30 Codes/2_figures_tables.rmd
minor updates

```{r}
plot_yield_data <-
  all_results[, .(crop, yield_pred_data)] %>%
  rowwise() %>%
  dplyr::mutate(plot_data = list(
    yield_pred_data[, crop_type := crop] %>%
      .[, crop_type := case_when(
        crop_type == "corn" ~ "A. Corn",
        crop_type == "soy" ~ "B. Sybean"
      )]
  )) %>%
  dplyr::mutate(sat_cat_text_ls = list(
    plot_data[, .(sat_rank, sat_cat_text)] %>%
      .[!is.na(sat_rank), ] %>%
      unique(by = "sat_rank") %>%
      .[order(sat_rank), sat_cat_text]
  )) %>%
  dplyr::mutate(plot_data = list(
    plot_data %>%
      .[is.na(sat_cat_text), sat_cat_text := "Rainfed"] %>%
      .[, sat_cat_text := factor(sat_cat_text, levels = c("Rainfed", sat_cat_text_ls))]
  ))

g_ir_yield_both <-
  plot_yield_data %>%
  dplyr::mutate(g_yield = list(
    ggplot(plot_data) +
      geom_line(aes(
        y = y_hat,
        x = balance,
        color = factor(sat_cat_text)
      )) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-2:11) * 100
      ) +
      scale_y_continuous(
        name = "Yield (tonne/ha)",
        breaks = 0:(ceiling(max(plot_data$y_hat)) + 0.5),
        limits = c(NA, (ceiling(max(plot_data$y_hat)) + 0.5))
      ) +
      scale_color_discrete(
        name = "Aquifer Thickness",
        guide = guide_legend(
          title.position = "top",
          nrow = 2
        )
      ) +
      scale_fill_discrete(guide = "none") +
      theme_fig +
      coord_cartesian(xlim = c(-200, 1150)) +
      theme(legend.position = "bottom")
  ))

@@

g_wds <-
  all_results[, .(crop, data)] %>%
  dplyr::mutate(g_fig = purrr::map(
    data,
    function(data) {
      ggplot(data) +
        geom_histogram(aes(x = balance), bins = 50, col = "darkgreen", fill = NA) +
        theme_fig +
        xlab("Water Deficit (mm)") +
        ylab("") +
        theme_void()
    }
  ))

g_wd_corn <-
  g_wds$g_fig[[1]] +
  ggtitle("A. Corn") +
  theme(plot.title = element_text(size = 9, family = "Times", face = "bold"))

g_wd_soy <-
  g_wds$g_fig[[2]] +
  ggtitle("B. Soybean") +
  theme(plot.title = element_text(size = 9, family = "Times", face = "bold"))

@@

@@

#++++++++++++++++++++++++++++++++++++
#+ With confidence interval (seprately)
#++++++++++++++++++++++++++++++++++++
g_yield_with_conf <-
  plot_yield_data %>%
  dplyr::mutate(plot_data = list(
    plot_data[, `:=`(
      lower = y_hat - 1.96 * y_hat_se_modeled,
      upper = y_hat + 1.96 * y_hat_se_modeled
    )]
  )) %>%
  dplyr::mutate(g_fig = list(
      ggplot(plot_data) +
        geom_ribbon(
          aes(
            ymin = lower,
            ymax = upper,
            x = balance
          ),
          alpha = 0.3
        ) +
        geom_line(aes(
          y = y_hat,
          x = balance
        )) +
        facet_wrap(~sat_cat_text, ncol = 2) +
        scale_x_continuous(
          name = "Water Deficit (mm)",
          breaks = (-1:5) * 200
        ) +
        scale_y_continuous(
          name = "Yield (tonne/ha)",
          breaks = 0:13
        ) +
        theme_fig +
        theme(
          legend.position = "bottom",
          strip.background = element_blank()
        )
  )) %>%
  dplyr::select(crop, g_fig) %>%
  data.table()

@@

g_share <-
  ggplot(plot_data_ir_share[sat <= 150, ]) +
  geom_line(aes(y = ir_share_hat, x = sat)) +
  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper,
      x = sat
    ),
    alpha = 0.4
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

@@

```{r}
g_share_dif <-
  ggplot(plot_data_ir_share[sat < 130, ]) +
  geom_line(aes(y = dif_ir_share_hat, x = sat)) +
  geom_ribbon(
    aes(
      ymin = dif_lower,
      ymax = dif_upper,
      x = sat
    ),
    alpha = 0.4
  ) +
  geom_hline(yintercept = 0, color = "red") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

@@

```{r}
g_ay_response <-
  all_results[, .(crop, avg_yield_sum)] %>%
  unnest(cols = c(avg_yield_sum)) %>%
  data.table() %>%
  .[, sat_text := paste0(
    "Aquifer Thickness = ",
    format(sat, digits = 3),
    "m"
  )] %>%
  .[sat != min(sat), ] %>%
  nest_by(crop) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data) {
    ggplot(data) +
      geom_ribbon(aes(x = balance, ymin = lower, ymax = upper), alpha = 0.3) +
      geom_line(aes(x = balance, y = avg_yield)) +
      facet_grid(. ~ sat_text, scales = "free_y") +
      ylim(min(data$avg_yield) * 0.7, max(data$avg_yield) + 1) +
      xlab("Water Deficit (mm)") +
      ylab("Yield (tonne/ha)") +
      theme_fig +
      theme(
        strip.background.x = element_blank(),
        panel.spacing = unit(0.1, "cm")
      )
  }))

>>>>

```{r}
# all_results <-  data.table(all_results)

plot_yield_data <-
  all_results[, .(crop, yield_pred_data)] %>%
  rowwise() %>%
  dplyr::mutate(plot_data = list(
    yield_pred_data[, crop_type := crop] %>%
      .[, crop_type := case_when(
        crop_type == "corn" ~ "A. Corn",
        crop_type == "soy" ~ "B. Sybean"
      )]
  )) %>%
  dplyr::mutate(sat_cat_text_ls = list(
    plot_data[, .(sat_rank, sat_cat_text)] %>%
      .[!is.na(sat_rank), ] %>%
      unique(by = "sat_rank") %>%
      .[order(sat_rank), sat_cat_text]
  )) %>%
  dplyr::mutate(plot_data = list(
    plot_data %>%
      .[is.na(sat_cat_text), sat_cat_text := "Rainfed"] %>%
      .[, sat_cat_text := factor(sat_cat_text, levels = c("Rainfed", sat_cat_text_ls))]
  ))

g_ir_yield_both <-
  plot_yield_data %>%
  dplyr::mutate(g_yield = list(
    ggplot(plot_data) +
      geom_line(aes(
        y = y_hat,
        x = balance,
        color = factor(sat_cat_text)
      )) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-2:11) * 100
      ) +
      scale_y_continuous(
        name = "Yield (tonne/ha)",
        breaks = 0:(ceiling(max(plot_data$y_hat)) + 0.5),
        limits = c(NA, (ceiling(max(plot_data$y_hat)) + 0.5))
      ) +
      scale_color_discrete(
        name = "Aquifer Thickness",
        guide = guide_legend(
          title.position = "top",
          nrow = 2
        )
      ) +
      scale_fill_discrete(guide = "none") +
      theme_fig +
      coord_cartesian(xlim = c(-200, 1150)) +
      theme(
        legend.position = "bottom",
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_blank()
      )
  ))

@@

g_wds <-
  all_results[, .(crop, data)] %>%
  dplyr::mutate(g_fig = purrr::map(
    data,
    function(data) {
      ggplot(data) +
        geom_histogram(aes(x = balance), bins = 50, col = "darkgreen", fill = NA) +
        theme_fig +
        xlab("") +
        ylab("") +
        # scale_x_continuous(breaks = (-2:11)*100) +
        coord_cartesian(xlim = c(-200, 1150))
        # +
        # # xlim(NA, max_balance) +
        # theme_void()
    }
  ))

g_wd_corn <-
  g_wds$g_fig[[1]] +
  ggtitle("A. Corn") +
  theme(
    plot.title = element_text(size = 9, family = "Times", face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    plot.margin = margin(0, 0, 0, 0, "cm")
  )

g_wd_soy <-
  g_wds$g_fig[[2]] +
  ggtitle("B. Soybean") +
  theme(
    plot.title = element_text(size = 9, family = "Times", face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    plot.margin = margin(0, 0, 0, 0, "cm")
    )

@@

# g_yield_response <-
#   cowplot::plot_grid(
#     g_wd_corn, g_ir_yield_corn,
#     ncol = 1,
#     align = "v",
#     rel_heights = c(0.15, 0.72)
#   )

# g_yield_response_soy <-
#   cowplot::plot_grid(
#     g_wd_soy, g_ir_yield_soy,
#     ncol = 1,
#     align = "v",
#     rel_heights = c(0.15, 0.72)
#   )

@@

#++++++++++++++++++++++++++++++++++++
#+ With confidence interval (seprately)
#++++++++++++++++++++++++++++++++++++
g_yield_with_conf <-
  plot_yield_data %>%
  dplyr::mutate(plot_data = list(
    plot_data[, `:=`(
      lower = y_hat - 1.96 * y_hat_se_modeled,
      upper = y_hat + 1.96 * y_hat_se_modeled
    )]
  )) %>%
  dplyr::mutate(g_fig = list(
      ggplot(plot_data) +
        geom_ribbon(
          aes(
            ymin = lower,
            ymax = upper,
            x = balance
          ),
          alpha = 0.3
        ) +
        geom_line(aes(
          y = y_hat,
          x = balance
        )) +
        facet_wrap(~sat_cat_text, ncol = 2) +
        scale_x_continuous(
          name = "Water Deficit (mm)",
          breaks = (-1:5) * 200
        ) +
        scale_y_continuous(
          name = "Yield (tonne/ha)",
          breaks = 0:14
        ) +
        theme_fig +
        theme(
          legend.position = "bottom",
          strip.background = element_blank()
        )
  )) %>%
  dplyr::select(crop, g_fig) %>%
  data.table()

@@

g_share <-
  ggplot(plot_data_ir_share[sat <= 150, ]) +
  geom_line(aes(y = ir_share_hat, x = sat)) +
  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper,
      x = sat
    ),
    alpha = 0.4
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Decline in Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

@@

```{r}
g_share_dif <-
  ggplot(plot_data_ir_share[sat < 105, ]) +
  geom_line(aes(y = dif_ir_share_hat, x = sat)) +
  geom_ribbon(
    aes(
      ymin = dif_lower,
      ymax = dif_upper,
      x = sat
    ),
    alpha = 0.4
  ) +
  geom_hline(yintercept = 0, color = "red") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

@@

```{r}
g_ay_response <-
  all_results[, .(crop, avg_yield_sum)] %>%
  unnest(cols = c(avg_yield_sum)) %>%
  data.table() %>%
  .[, sat_text := paste0(
    "Aquifer Thickness = ",
    format(sat, digits = 3),
    "m"
  )] %>%
  .[sat != min(sat), ] %>%
  nest_by(crop) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data) {
    ggplot(data) +
      geom_ribbon(aes(x = balance, ymin = lower, ymax = upper), alpha = 0.3) +
      geom_line(aes(x = balance, y = avg_yield)) +
      facet_grid(. ~ sat_text, scales = "free_y") +
      ylim(min(data$lower) * 0.7, max(data$upper) + 1) +
      xlab("Water Deficit (mm)") +
      ylab("Yield (tonne/ha)") +
      theme_fig +
      theme(
        strip.background.x = element_blank(),
        panel.spacing = unit(0.1, "cm")
      )
  }))
